A Simple Minibatch Acceptance Test for MCMC

### 2016-05-19 nips_2016.tex
OK Haoyu was using a constant temperature after all. Finally clarified the confusion. Lets use this as the first NIPS submission

We next use logistic regression for the binary classification of 1s versus 7s in the MNIST
dataset~\cite{lecun-mnisthandwrittendigit-2010}. The data has 12007 and 1000 training and testing
points, respectively (we used a random subset of the test data). The propose is again a random walk
with covariance matrix $0.1I$ for the $784\times 784$ identity matrix $I$. We initialize the
posterior temperature at $T_0=3000$, and decrease it according to $T_i = T_0 /(i + 1)^{3}$ for $i
\leq N/2$ and $T_i = T_0 /(i + 1)^{0.2}$ for $i >N/2$, where $N=4000$ is the total number of
iterations. We set the minibatch size $m=50$ and compare with adaptive sampling.

@@

For our minibatch MH test, in order to enforce the ${\rm std}(\Delta') < 1.2$ condition, we
initialize the temperature $T_0 = 3000$, and decrease it by the rule $T_i = T_0 /(i + 1)^{3}$ for $i
\leq N/2$ and $T_i = T_0 /(i + 1)^{0.2}$ for $i >N/2$, where $N=4000$ is the total number of
iterations. If our estimated ${\rm std}(\Delta') \ge 1.2$, we ignore the current iteration.
Figure~\ref{fig:appendixExp2} plots our estimated ${\rm std}(\Delta')$ values versus iteration
count.

>>>>

We next use logistic regression for the binary classification of 1s versus 7s in the MNIST
dataset~\cite{lecun-mnisthandwrittendigit-2010}. The data has 12007 and 1000 training and testing
points, respectively (we used a random subset of the test data). The propose is again a random walk
with covariance matrix $0.1I$ for the $784\times 784$ identity matrix $I$. We set the posterior
temperature at $T=3000$. We set the minibatch size $m=50$ and compare with adaptive sampling.

@@

For our minibatch MH test, in order to enforce the ${\rm std}(\Delta') < 1.2$ condition, we use a
constant temperature $T = 3000$. If our estimated ${\rm std}(\Delta') \ge 1.2$, we ignore the
current iteration.  Figure~\ref{fig:appendixExp2} plots our estimated ${\rm std}(\Delta')$ values
versus iteration count.
